---
title: "**PCFL 2025: Week 12 wrap-up**"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 4
    theme: united
editor: source
execute:
  echo: true
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| include: false
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(showtext)

setwd(here::here())

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()
week_sel=2

source("scripts/league_data.R")
```

Welcome back! It's good to be back on the field again. Let's check in and see how the first two weeks of the season have gone.

## Last week's games

```{r}
#| echo: false
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Some real powerhouse performances from the usual suspects: Henry's Gonna Cook and Sasquatch. Captain Clairvoyant also with a nice game.

## Best performances

### Best players overall
Here's last week's **10 best performing players.** 

```{r}
#| echo: false
kable(top_n(starters,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r}
#| echo: false
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=`PCFL Team`))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```


```{r}
#Season bench standings

#| eval: false
#| echo: false
 kable(starter_benchteam_all %>%
         arrange(-`Bench points`) %>%
 rename(Team=name))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Waiver masters

I've tallied the players picked up by each team since the draft and the points they've contributed as starters. Here's where those stand.

```{r}
#| echo: false
kable(roster_pickup %>%
        select(-abbrev) %>%
        rename(Team=name,Points=draftpoints,
               Transactions=draft_num) %>%
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Sasquatch has always been a waiver master.

### Recapping the draft
Here's the amount of points drafted players have contributed to each team as starters.

```{r}
#| echo: false
kable(roster_draft %>% 
         select(-abbrev) %>%
        rename(Team=name,Points=draftpoints) %>% 
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best team performances 

Here's a list of the **top five scoring performances** so far this (young) season.

```{r}
#| echo: false
kable(toppoints %>%
        arrange(-Score))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

## Looking ahead

### League standings

Our league standings are a little unusual. We rank teams based on points, kinda like hockey. There are two ways to get points:

* Win your weekly matchup (1 point)
* Finish in the top six point scorers (1 point)

```{r}
#| echo: false
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### If the season ended today...

It's too early, y'all!

### This week's matchups

```{r}
#| echo: false
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Good luck, y'all. Check your injuries!
