---
title: '**PCFL 2022: Week 9 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-9

source("scripts/league_data.R")

```

Hey all! We've got just six weeks to go in the regular season. Fantasy life moves fast.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I've already whined on GroupMe about my narrow loss to Erin & Trav in part due to Kenyan Drake, who was on wavers just 48 hours before beating me. Sigh.

Sarah had a second huge week points wise, this time powered by Joe Mixon, and got Jacob's GOAT. Jacob, by the way, had THREE starters who were on bye and still got nearly 100 points.

Other winners last week were Scott, Brian, and Evan.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Already mentioned Joe Mixon. Disappointing last week, but a very nice performance this week. A couple of break out running backs (Walker and Etienne) as well as Kenyan Drake's two touchdown day.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Crissy's top scorer this week was a kicker. And for the Hobbits it was the New England Defense. Not sure what that all means.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott edged out Jacob this week.

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

Still Scott and Evan at the top for both actual and optimized points, but both have left a lot on the table. Jacob's gap is particularly notable as well.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Shoula coulda woulda played Justin Fields this week, but these things are unpredictable. Is there a better redemption story this season that Geno Smith and the Seahawks?

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Sarah has two spots in the top five. She also only has two wins (and seven losses). Again, not sure what that means.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Evan remains our leader this week with his win, but both Scott and Robbie aren't far behind. There's a bunch of fighting for that last playoff spot.

### If the season ended today...

Here's where this starts to get real, y'all. I've been thinking through both ESPN's rankings and our point system as we go. My inclination is that playoffs would be decided based on the latter--the "team points" column-as I see that as being a fairer judge of team performance than just wins and losses. I'd keep the division winner/wildcard designations, though 

Here's what this would look like right now: 
* Division winners: Evan (14 points, Grits), and Scott (13 points, Hot Dish). 
* Wild cards: Robbbie (12 points) and Jacob (8 points and a points scored tie breaker)

The ESPN version would still be Evan and Scott as division winners, but the wildcards would be Robbie and Erin/Trav based on wins.

****If you have concerns about this system, let me know ASAP****

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

A good mix of games next week. As things start to get serious for the playoffs, we'll see if Sarah can keep her hot streak going against Crissy. Richard had a VERY tough week last week, but he'll try to take a bit out of Brian's playoff dreams. Evan and Jacob face off in the Covenant youth bowl. There may be snow for the Minnesotan matchup of Scott and Erin/Trav. Lastly, I'll try to stay alive for the playoffs against Robbie.

Good luck, y'all! (And check your byes!)