---
title: '**PCFL 2022: Week 10 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-10

source("scripts/league_data.R")

```

Hey all! We've got just five weeks to go in the regular season. Fantasy life moves fast.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The top game last week was The Juniors versus the Hobbits, a purely Minnesota battle. It was a high scoring affair between the two top point-scorers this week, but Erin and Trav came out on top in the end.

In other games, Evan took his second loss against Jacob, and the Jumpin' Jaheims were actually LAST in points scored this week. Brian beat Richard, and I won a tight match against Robbie. The Gophers topped the Sharks in a contest between Toilet Trophy winners.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Nice week for several wide receivers.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I'm starting Justin Fields this week, as he was the top scorer in the league while on my bench. Cole Kmet turned it on for the Gophers, and it's not often that tight ends make this list.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Hurray for the Peanuts!

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott's still in the lead here.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

Still Scott and Evan at the top for both actual and optimized points, but both have left a lot on the table. Jacob's gap remains the largest.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The bye weeks mean lots of quarterbacks and tight ends on the waiver wire. None did particularly well, though Dalton Schultz was respectable for Brian. 

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

No changes this week.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott and Evan are now tied for tops in the leagu, with Robbie solidly in third. It's a three team tie for the fourth spot (me, Crissy, and Erin/Trav). Sarah and Richard are now fighting it for the toilet trophy.

### If the season ended today...

Here's our playoff picture  right now: 
* Division winners: Evan (14 points, Grits), and Scott (14 points, Hot Dish). 
* Wild cards: Robbie (12 points) and me (10 points and a points scored tie breaker)

The ESPN version would still be Evan and Scott as division winners, but the wildcards would be Robbie and Erin/Trav based on wins.

****If you have concerns about this system, let me know ASAP****

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It's a family battle this week between Sarah and Erin (and Trav), as the sisters face off in what may be a high scoring battle. Evan tries to break his team slump against Crissy. Brian tries to get into the playoff picture against Jacob and Richard does the same against Robbie. Lastly, my running back situation is dire, but I'll do my best against our points leader, Scott.

Good luck, y'all! (And check your byes!)