---
title: '**PCFL 2022: Week 2 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)

week_sel<-2

source("scripts/league_data.R")

```

It's the first week of the new season! Great to be back playing with you all.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Last week's game of the week was The Jaheims versus the GOAT, and it was a good one, with both teams ending up in the top 5 in scoring. Evan's team came out on top, though. 

The real barn burner of the week was the Peanuts vs the Hobbits (both mighty despite their diminutive names). Scott led the league in scoring last week and was second this week. Unfortunately for him, Jalen Hurts and Stefan Diggs pushed me to a late victory and the top scoring spot for the week.

In other action, Brian topped Richard and Robbie's Bigfoot squeaked by Crissy's Gophers. In a family battle, Erin and Trav bested older sister Sarah, sending the latter to an 0-2 start and early trade action.

## Best performing players

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

# kable(top_n(players %>% 
#               select(name,points,fullname),10,points) %>%
#         rename(Player=name,
#                Points=points,
#                Team=fullname) %>%
#         arrange(-Points))
```

Lamar Jackson! The Baltimore QB led this week's performances with >40 points. Following behind were three well-known wide receivers: Diggs, Hill, and Waddle. And our DGD Bulldog of the week is Nick Chubb with a solid performance. 

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

There are...a lot of bench players on this list. Scott can be excused for not starting Tua, who had a great week. But Amari Cooper, Drake London, and Christian Kirk would all have been solid starters, though each were at just a modest 20 point mark.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott was the clear leader this week, and I had to look to see whether Brian actually had more than one player on his bench.

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Erin/Trav and Scott neck and neck at this point.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Curtis Samuel and Johan Dotson were notable additions this week.


## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Here's where things start to get interesting. We have two 2-0 teams: Jumpin' Jaheims and Athens Team Sasquatch. However, Robbie's team this week wasn't in the top 5 in scoring, so he only got one "team point." Scott's Hobbits were a tough luck loss this week, so even though he's 1-1, he is still tied in team points with Robbie. 

As it stands, Evan's at the top of these (early) standings, and Sarah has the early lead in the race for the toilet trophy.


```{r, echo=FALSE}
# Here's a list of the **top five scoring performances** so far this season.

# kable(toppoints %>%
#         rename(Team=fullname,
#                Week=week,
#                `Points scored`=points_scored,
#                Result=result))
```


```{r eval=FALSE, echo=FALSE, message=FALSE}
#Lastly, here's a look at the **points trendline** for each team.

# teamtrend<-results %>%
#   select(awayteam,awaypoints,week) %>%
#   rename(teamId=awayteam,
#          points=awaypoints) %>%
#   bind_rows(results %>%
#               select(hometeam,homepoints,week) %>%
#               rename(teamId=hometeam,
#                      points=homepoints)) %>%
#   mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
#   left_join(team_list %>%
#               select(teamId,fullname))
# 
# ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
#   geom_line()+
#   geom_point(col="red")+
#   #geom_smooth()+
#   facet_wrap(~fullname)
```

### If the season ended today...

Only week 2, but based on team points, our playoff field right now would be Evan, Scott, Jacob, and Robbie. I would replace Jacob as the last playoff team in traditional scoring (record + points tiebreaker)

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

This week's game of the week is clearly the Jumpin Jaheims vs. the Hangry Hobbits, the top of the rankings versus our highest scoring offense thus far. Our family matchup is Peanuts vs. Sharks (pray for us, y'all). Good luck, y'all!