---
title: '**PCFL 2022: Week 8 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()


week_sel<-8

source("scripts/league_data.R")

```

Last week was ANOTHER week with no recap, but the travel's over, so I should be back in the saddle the rest of the season.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

My guys have been up and down this year, but this was a BIG week for the Georgia Peanuts, ending Evan's time as the last undefeated team. We also had a shootout between the Sasquatch and the Sharks, who ended up 1 and 2 in scoring as Robbie came out on top. The Hobbits also dominated, and Erin/Trav eked out a win against Jacob.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Alvin Kamara had an Alvin Kamara week, and Christian McCaffrey didn't take long to settle in with his new team.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Pretty much everyone made the starting lineup here, except for Kirk Cousins on the Gophers.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Go Gophers!

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}

ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))

# actual_rank<-actualpoints %>% 
#          group_by(Week) %>%
#          mutate(`Optimization rate`=as.numeric(str_replace(`Optimization rate`,"%","")),
#                 Week=paste("Week ",as.character(Week),sep=""),
#                 Rank=row_number()) %>%
#   arrange(-Rank)
# 
# ggplot(actual_rank,
#        aes(x=Rank,y=`Optimization rate`,fill=`PCFL Team`)) +
#   geom_bar(stat="identity",position="dodge") + 
#   xlab("")+
#   scale_fill_brewer(palette="Paired")+
#   theme_minimal()+
#   theme(axis.ticks.x=element_blank(),
#         axis.text.x=element_blank(),
#         text=element_text(family="Source Sans Pro"),
#         strip.text.x = element_text(size = 12,family="Source Sans Pro Semibold"))+
#   facet_wrap(~`Week`)
```

Scott and Evan looking good here, though Robbie and me have been pretty efficient with what we have.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Redemption week for DJ Moore.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

We've got *TWO* new names at the top with Robbie and Sarah. Bummer that Sarah's came against Robbie, as she would have one literally ANY other matchup so far this season.

```{r eval=FALSE, echo=FALSE, message=FALSE}
#Lastly, here's a look at the **points trendline** for each team.

# teamtrend<-results %>%
#   select(awayteam,awaypoints,week) %>%
#   rename(teamId=awayteam,
#          points=awaypoints) %>%
#   bind_rows(results %>%
#               select(hometeam,homepoints,week) %>%
#               rename(teamId=hometeam,
#                      points=homepoints)) %>%
#   mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
#   left_join(team_list %>%
#               select(teamId,fullname))
# 
# ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
#   geom_line()+
#   geom_point(col="red")+
#   #geom_smooth()+
#   facet_wrap(~fullname)
```


## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Evan remains on top even with the loss last week. However, Scott still has the points lead. I've added the points per game average for the last three weeks to see how teams are trending up (Robbie, me, Richard, Sarah) or down (Erin/Trav, Crissy, Jacob).

### If the season ended today...

Current playoff teams (ESPN): Evan and Scott as division winners, Robbie and me as wildcards

Current playoff teams (Team points): Evan, Robbie, Scott, and Jacob

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

We'll see if Evan can get on track next week against the suddenly surging Pigskin on the Gridiron. Scott tries to knock Crissy out a playoff spot. Robbie and Brian face off in a matchup of playoff perennials. Sarah tries to make up some ground against the fading GOAT, and I face off against Erin and Trav.

Good luck, y'all! (And check your byes!)