---
title: 'PCFL: Week 8 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) > today()) %>%
  filter(mdy(Date)==min(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/league_schedule.csv")
team_list<-read_csv("data/league_roster.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))

nextweek_long<-schedule %>%
  filter(week==week_sel) %>%
  mutate(gameid=row_number()) %>%
  pivot_longer(away_id:home_id,
               names_to="awayhome",
               values_to="teamId") %>%
  left_join(team_list %>% 
              select(teamId,fullname)) %>%
  left_join(stand_tbl %>%
              select(fullname,points_scored)) %>%
  select(-teamId) 

nextweek<-nextweek_long %>%
  filter(awayhome=="away_id") %>%
  rename(away_team=fullname,
         away_points=points_scored) %>%
  left_join(nextweek_long %>%
              filter(awayhome=="home_id") %>%
              select(-awayhome) %>%
              rename(home_team=fullname,
                     home_points=points_scored)) %>%
  mutate(range=abs(away_points-home_points)) %>%
  select(-gameid,-awayhome) 

```

### Last week's games

```{r, echo=FALSE}
kable(last_week %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints))
```

A bit of a low scoring week this week (aside from one outlier!). We had both extremes, though. The Peanuts shelled the First Timers, winning by nearly 100 points. At the other end, the Sharks nibbled just enough of Team Sasquatch to secure a victory against the league leaders. In our family game of the week, Richard scored a convincing win, as Jacob's G.O.A.T. struggled to dig out of an offensive slump. Christine's Gophers also dug out the Jaheims, winning by over 20 points.

Obligatory reminder: you should make sure to check your bye weeks and also whether your stars are active at gametime.

#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Dalvin Cook (along with Davante Adams) powered the Peanuts' dominant performance this week. Some other usual suspects at quarterback also make the list: Mahomes, Wilson, Rodgers, and Stafford. DK Metcalf also had a standout week for Brian's squad.

#### Best addition and worst starters
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

While there were a lot of pickups last week, they didn't have a whole lot of payoff. The exceptions were Giovani Bernard, the veteran who provided a nice boost for Sarah. Brandon Aiyuk was another nice pickup for the Gophers. 

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

### League standings and season stats
Here's a look at our current standings

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Georgia Peanuts
* D-FENCE (least points allowed): KC Gophers
* Tough luck (points rank - playoff rank): Hangry Hobbits (5th in points, 9th in the standings) and the First Timers (3rd and 7th)
* Lucky ducks (playoff rank - points rank): KC Gophers (9th in points, 6th in the standings)

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

The Peanuts roasted the competition last week.

Lastly, here's a look at the **points trendline** for each team.

```{r, echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=as.character(week)) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```


## Next week's games

Here's a quick summary of next week's matchups:

```{r,echo=FALSE}
kable(nextweek)
```

We're reaching a point in the season where the playoffs begin to loom on the horizon, and the Hobbits and Jaheims could really use a win to stay in the hunt. They'll try to do so against Pigskin on the Gridiron and the G.O.A.T respectively. At the top of the standings, Sarah will try to knock off Brian--the other league leader, while Erin and Trav tag team against Team Sasquatch. Good luck all!
