---
title: 'PCFL: Week 15 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) > today()) %>%
  filter(mdy(Date)==min(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/league_schedule.csv")
team_list<-read_csv("data/league_roster.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))

nextweek_long<-schedule %>%
  filter(week==week_sel) %>%
  mutate(gameid=row_number()) %>%
  pivot_longer(away_id:home_id,
               names_to="awayhome",
               values_to="teamId") %>%
  left_join(team_list %>% 
              select(teamId,fullname)) %>%
  left_join(stand_tbl %>%
              select(fullname,points_scored)) %>%
  select(-teamId) 

nextweek<-nextweek_long %>%
  filter(awayhome=="away_id") %>%
  rename(away_team=fullname,
         away_points=points_scored) %>%
  left_join(nextweek_long %>%
              filter(awayhome=="home_id") %>%
              select(-awayhome) %>%
              rename(home_team=fullname,
                     home_points=points_scored)) %>%
  mutate(range=abs(away_points-home_points)) %>%
  select(-gameid,-awayhome) 

```

### Recapping the first round

```{r, echo=FALSE}
kable(last_week %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints))
```

Last week was the first round of the playoffs, and both Robbie and I had comfortable wins. As a result, this year's champtionship is a repeat from last year, though I was the underdog in that one points wise. Jacob and Brian will be fighting it out for third place.

In the consolation brackets, Erin & Trav edged out Christine to stay in the mix for fifth. They'll be playing Richard, who had a comeback win late Monday against Sarah. Evan escaped the last place game by beating Scott. 

#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Noone expected much from Jalen Hurts, including me, which is why he was on my bench. But he was up there with Josh Allen and Ryan Tannehill for top performances of the week. Tony Pollard and a surprisingly resurgent David Montgomery topped the non-QB list.

#### Best addition and worst starters
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

We're now very late in the season, but Baker Mayfield has also come on strong as a QB. 

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

It was a tough week for Brian, as he had a lot of great RB play on his bench but needed the WR to come through as well. 

### Tracking the standings

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Georgia Peanuts
* D-FENCE (least points allowed): Southern Sharks


Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

There were unchanged from last week. Will anyone break into the top 5 in our final contests?

Lastly, here's a look at the **points trendline** for each team.

```{r, echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14,15,16))) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```

### Championship week!

The championship game is set: The Peanuts against the Sasquatch. My points have been trending down and most of my RB got hurt last week, so we'll see how this one plays out.

Here's the lineup for other games:

* Third place: GOAT (Jacob) vs. Captain Clairvoyant (Brian)
* Fifth place: First Timers (Erin/Trav) vs. Pigskin on the Gridiron (Richard)
* Seventh place: Jumpin' Jaheims (Evan) vs. KC Gophers (Christine)
* Last place: Southern Sharks (Sarah) vs. Hangry Hobbits (Scott)

Sad we can't have a year end party this year, but thanks for a fun season. Good luck to everyone!
