---
title: 'PCFL: Week 6 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)

week_sel<-6

#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/league_schedule.csv")
team_list<-read_csv("data/league_roster.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))

nextweek_long<-schedule %>%
  filter(week==week_sel+1) %>%
  mutate(gameid=row_number()) %>%
  pivot_longer(away_id:home_id,
               names_to="awayhome",
               values_to="teamId") %>%
  left_join(team_list %>% 
              select(teamId,fullname)) %>%
  left_join(stand_tbl %>%
              select(fullname,points_scored)) %>%
  select(-teamId) 

nextweek<-nextweek_long %>%
  filter(awayhome=="away_id") %>%
  rename(away_team=fullname,
         away_points=points_scored) %>%
  left_join(nextweek_long %>%
              filter(awayhome=="home_id") %>%
              select(-awayhome) %>%
              rename(home_team=fullname,
                     home_points=points_scored)) %>%
  mutate(range=abs(away_points-home_points)) %>%
  select(-gameid,-awayhome) 

```

### Last week's games

```{r, echo=FALSE}
kable(last_week %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints))
```

This was a week of nail-biters, with all but one contest determined by 10 points or less. My Peanuts just avoided getting roasted by the Hobbit's fire. The First Timers couldn't quite jump the (Southern) Sharks. Captain Clairvoyant was able to dig out the Gophers, and Richard's Pigskin team continued to slide, getting spiked by Team Sasquatch. The one easy win this week was Jacob's group living up to their name. 

Everyone but Evan scored between 100 and 115 points this week. #parity

#### Best performing players

Here's last week's **10 best performing players.** The bench variable shows whether they got left on the bench or not.

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname,bench),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname,
               `Benched`=bench) %>%
        arrange(-Points))
```

Derrick Henry had a breakout week, as did the rookie Justin Jefferson for the Vikings (though on the bench). The Atlanta offense also had some top players in Matt Ruan and Julio Jones.

#### Best addition and worst starters
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Let's hear it for the kickers! Younghoe Koo was the top new add (and a key part of my victory). Brian, Robbie, and Sarah also had good adds. It's the time of year when some folks are streaming defenses, and the Dolphins were a nice pickup by Richard.


Who should have been **left on the bench** this week--the lowest points scored by starters?

```{r,echo=FALSE}
kable(top_n(players %>% 
              filter(bench==0) %>%
              select(name,points,fullname),5,-points) %>%
      rename(Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(Points))
```

Another week, another defense with negative points. Some other names were on bye and added before I updated stats.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

Erin and Trav could have used some of those 107 points, as their bench outscored their starters this week.

### League standings and season stats
Here's a look at our current standings

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): First Timers
* D-FENCE (least points allowed): KC Gophers
* Tough luck (points rank - playoff rank): The First Timers
* Lucky ducks (playoff rank - points rank): Team Sasquatch

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

This is unchanged since last week.

Lastly, here's a look at the **points trendline** for each team.

```{r, echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=as.character(week)) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```


## Next week's games

Here's a quick summary of next week's matchups:

```{r,echo=FALSE}
kable(nextweek)
```

Another good matchup on tap between Captain Clairvoyant and Team Sasquatch. The potential mismatch of the week is the suddenly vulnerable First Timers against the Jumpin' Jaheims. Good luck all! (And remember to check your bye weeks.)
