---
title: 'PCFL 2021: FINAL WEEK wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(lubridate)
library(purrr)
library(gghighlight)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) < today()) %>%
  filter(mdy(Date)==max(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/leaguesched.csv")
team_list<-read_csv("data/teaminfo1.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))
nextweek<-read_csv(paste("data/nextweek_wk",week_sel,".csv",sep=""))

# lastweek_line<-read_csv(paste("data/nextweek_wk",week_sel-1,".csv",sep="")) %>%
#   select(away_team:range) %>%
#   mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
#          range=abs(away_points-home_points)) %>%
#   mutate(Favored=if_else(away_points>home_points,
#                          paste(away_team," (+",round(range,2),")",sep=""),
#                          paste(home_team," (+",round(range,2),")",sep=""))) %>%
#   select(-range,-away_points,-home_points)

benchpoints_files<-paste("data/",list.files(path = "data",pattern="benchpoints"),sep="")
benchpoints_sum<-map_df(benchpoints_files,read_csv) %>%
  group_by(fullname) %>%
  summarise(points=sum(points))
```

### Last week's games

```{r, echo=FALSE, message=FALSE}
kable(last_week %>%
        #left_join(lastweek_line) %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints,
               #`Predicted result`=Favored
               ))
```

Another season in the books! Robbie had a disappointing week after such a strong season, but I was happy to see my Peanuts finish strong. In a low-scoring affair, Richard took third place over the Sophomores, who did slump a little at the end. The Sharks took a big bite out of Captain Clairvoyant for fifth place. Evan had a nice showing for seventh, and the Gophers convincingly took last.

#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

There's Ja'Maar Chase and then everyone else. Penny and St. Brown were both late season pickups for me, but the young players finished strong given the opportunity.

#### Best addition and top bench
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Nice job, Sharks! Not a lot of transactions this week, but Sarah had a couple good pickups.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

The Southern Sharks edged out my Peanuts by just 0.08 points.

Who has the most bench points for the _season_? Here's the final standings:

```{r,echo=FALSE}
kable(benchpoints_sum %>% 
        arrange(-points) %>%
        rename(`Team name`=fullname,`Total bench points`=points)) 
```

This one was a horse race at the end! Sarah and Robbie were clearly ahead of the pack, and Robbie won by just five points. Takes a bit of the sting out of the championship loss.

### League standings and season stats
Here's a look at the final standings.

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Georgia Peanuts **new**--finishing strong, the leader in both points and wins.
* Tough luck (points rank - playoff rank): Giving this one to Brian, who probably deserved to make the playoffs.
* Lucky ducks (playoff rank - points rank): Technically not stil me, but given that I occupied this spot for much of the season, probably the best candidate. Evan also finished with a playoff rank higher than his points.

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

I was hoping for a bigger night from Nick Chubb to take the top spot here, but my week 17 finished in 4th place for the season.

### Here's a look at the **points trendline** for each team.

```{r echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14,15,16,17))) %>%
  left_join(team_list %>%
              select(teamId,fullname)) %>%
  group_by(week) %>%
  mutate(weekmdn=median(points))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  geom_smooth(method="glm")+
  facet_wrap(~fullname)
```

Here's a NEW graph showing relative standing by week. The y axis is total points relative to the league mean (so negative is below the mean, positive is above).

```{r, echo=FALSE}
teamtrend_cum<-teamtrend %>%
  group_by(fullname) %>%
  arrange(week) %>%
  mutate(points_all=cumsum(points)) %>%
  group_by(week) %>%
  mutate(points_all_mean=mean(points_all),
         points_all_adj=points_all-points_all_mean)

ggplot(teamtrend_cum) +
  geom_hline(yintercept=0)+
    geom_line(aes(x=week, y=points_all_adj,
                 color=fullname,group=fullname),lwd=1) +
  gghighlight(use_direct_label=FALSE) +
  theme_minimal() +
  xlab("Week") + ylab("Total points - league mean") +
  facet_wrap(~ fullname,labeller = label_wrap_gen(20))

# ggplot(teamtrend_cum)+
#  geom_line(alpha=0.3,aes(x=week,y=points_all,group=fullname))+
#  geom_point(alpha=0.8,aes(x=week,y=points_all,color=fullname))+
#  labs(color='Team') 
```

Here's the graph with all teams together:
```{r, echo=FALSE}
ggplot(teamtrend_cum) +
  geom_hline(yintercept=0)+
    geom_line(aes(x=week, y=points_all_adj,
                 color=fullname,group=fullname),lwd=1) +
  gghighlight(use_direct_label=FALSE) +
  theme_minimal() +
  theme(legend.title = element_blank())+
  xlab("Week") + ylab("Total points - league mean")
```


My last few weeks defeinitely stand out here. The GOAT and Gophers had, well, rough ends to the season.

### Quarter season winners

Lastly, let's take a look at standings by section of the season. We had seventeen weeks, so what if we break those into groups of four?

```{r,echo=FALSE}
# nextweek1<-nextweek %>% select(away_team:range) %>%
#   mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
#          range=abs(away_points-home_points)) %>%
#   mutate(Favored=if_else(away_points>home_points,
#                          paste(away_team," (+",round(range,2),")",sep=""),
#                          paste(home_team," (+",round(range,2),")",sep=""))) %>%
#   select(-range)
# names(nextweek1)<-c("Away team","Last 3 wks avg (away)","Home team","Last 3 wks avg (home)",
#                    "Line")
# kable(nextweek1)
```

Quarter 1 (Weeks 1-4):

```{r,echo=FALSE}
teamtrend_q1<-teamtrend %>%
  ungroup() %>%
  filter(week %in% c(1,2,3,4)) %>%
  group_by(fullname) %>%
  summarise(allpoints=sum(points)) %>%
  select(fullname,allpoints) %>%
  arrange(-allpoints) 

knitr::kable(teamtrend_q1)
```

Quarter 2 (Weeks 5-8):

```{r,echo=FALSE}
teamtrend_q2<-teamtrend %>%
  ungroup() %>%
  filter(week %in% c(5,6,7,8)) %>%
  group_by(fullname) %>%
  summarise(allpoints=sum(points)) %>%
  select(fullname,allpoints) %>%
  arrange(-allpoints) 

knitr::kable(teamtrend_q2)
```

Quarter 3 (Weeks 9-12):

```{r,echo=FALSE}
teamtrend_q3<-teamtrend %>%
  ungroup() %>%
  filter(week %in% c(9,10,11,12)) %>%
  group_by(fullname) %>%
  summarise(allpoints=sum(points)) %>%
  select(fullname,allpoints) %>%
  arrange(-allpoints) 

knitr::kable(teamtrend_q3)
```

Quarter 4 (Weeks 13-17)

```{r,echo=FALSE}
teamtrend_q4<-teamtrend %>%
  ungroup() %>%
  filter(week %in% c(13,14,15,16,17)) %>%
  group_by(fullname) %>%
  summarise(allpoints=sum(points)) %>%
  select(fullname,allpoints) %>%
  arrange(-allpoints) 

knitr::kable(teamtrend_q4)
```

Gotta play all four quarters, y'all!

This was a fun season. Hoping to catch up with you all at the season ending party and do this again next year.