---
title: 'PCFL 2021: Week 3 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(lubridate)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) < today()) %>%
  filter(mdy(Date)==max(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/leaguesched.csv")
team_list<-read_csv("data/teaminfo1.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))
nextweek<-read_csv(paste("data/nextweek_wk",week_sel,".csv",sep=""))
```

### Last week's games

```{r, echo=FALSE}
kable(last_week %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints))
```

The marquee matchup this week was last year's champion Sasquatch up against this year's early leader, Pigskin on the Gridiron. The result wasn't particularly close, with Richard leading decisively. He wasn't the weekly points leader, though. Evan's Jumpin' Jaheims took that honor, winning by 14 points over the #2 team this week, Scott's Hungry Hobbits. Tough loss, Scott. 

The G.O.A.T. is continuing an early skid. Jacob had more points this week, but not enough to best Brian's Captain Clairvoyant. The Sophomores are this season's Cinderella team thus far, not high in the points rankings but still undefeated. Sarah's Sharks had a rough week, as I won our inter-family matchup and broke 100 points for the first time this season.


#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Josh Allen and Justin Herbert were this week's QB heroes, with Matthew Stafford and Tom Brady not far behind. Mike Williams, Cooper Kupp, and Davante Adams were the top WRs, and Ezekiel Elliot and Kareem Hunt represented the RBs. 

#### Best addition and top bench
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Ouch. Cordarrelle Patterson was the only new player to score more than 5 points this week, and the Panthers Defense barely got into double digits. Not a good week on the waiver wire.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

Robbie could have used some of the points on his bench, as he had the top scoring group this week by 20 points.

### League standings and season stats
Here's a look at the current standings.

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Pigskin on the Gridiron
* D-FENCE (least points allowed): The G.O.A.T.
* Tough luck (points rank - playoff rank): Middle Earth Hangry Hobbits *new*--third in points, but only sixth in the rankings.
* Lucky ducks (playoff rank - points rank): The Sophomores--still undefeated but only 7th in the points rankings. How long will their luck hold?

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

Evan's jumped up to third on the list with his performance last week.

### Here's a look at the **points trendline** for each team.

```{r echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```

The Sasquatch, Gophers, and Sharks aren't headed in the right direction, while Evan and I are trending up. 

### If the season ended today...

Our playoff teams would be Richard, Erin/Trav, Brian, and Evan. Our last place finisher would be Jacob. But it's still early!

### Next week's preview

```{r,echo=FALSE}
kable(nextweek)
```

It's a battle of undefeateds, as Richard goes up against Erin/Trav. There can only be one. Elsewhere, it's Scott vs. Sarah, Evan vs. Brian, Christine vs. me, and Brian vs. Jacob.

Good luck, y'all!
