---
title: 'PCFL 2021: Week 8 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

We're now over halfway through our regular season! Playoffs start in seven weeks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(lubridate)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) < today()) %>%
  filter(mdy(Date)==max(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/leaguesched.csv")
team_list<-read_csv("data/teaminfo1.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))
nextweek<-read_csv(paste("data/nextweek_wk",week_sel,".csv",sep=""))

lastweek_line<-read_csv(paste("data/nextweek_wk",week_sel-1,".csv",sep="")) %>%
  select(away_team:range) %>%
  mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
         range=abs(away_points-home_points)) %>%
  mutate(Favored=if_else(away_points>home_points,
                         paste(away_team," (+",round(range,2),")",sep=""),
                         paste(home_team," (+",round(range,2),")",sep=""))) %>%
  select(-range,-away_points,-home_points)


```

### Last week's games

```{r, echo=FALSE, message=FALSE}
kable(last_week %>%
        left_join(lastweek_line) %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints,
               `Predicted result`=Favored))
```

It was a tough week for a lot of teams last week! Five teams failed to break the century mark, and four were under 80. The defensive battle of the week was Sarah vs. Jacob, with The GOAT coming out on top despite only scoring 76 points. The biggest margin of victory last week was Captain Clairvoyant, who bested Team Sasquatch by more than 50 points. 

I went into Monday night needing only 3 points to beat Erin & Trav, but Khalil Herbert couldn't overcome David Montgomery's return. In other action, Scott's Hobbits beat Christine's Gophers, and Evan's Jumpin' Jaheims came out on top of Richard for the shootout of the week.

Last week's model came out 3-2. It's a work in progress, y'all.


#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

#### Best addition and top bench
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Lots of adds, but not a lot of action. Nyheim Hines scored 20 as the new addition on Richard's team, and the Patriots D was a big part of The Sophomore's victory

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

For the second straight week, Sarah's bench dominated--nearly TWICE as much as the 2nd place Hangry Hobbits. Here's a look at our *_new_* hot bench season point totals:

```{r,echo=FALSE}

```




### League standings and season stats
Here's a look at the current standings.

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Team Sasquatch
* D-FENCE (least points allowed): Georgia Peanuts *new*
* Tough luck (points rank - playoff rank): Hangry Hobbits *new*--now third in points but only sixth in the rankings
* Lucky ducks (playoff rank - points rank): We've got a three team tie here this week: Pigskin on the Gridiron (4th in points, 2nd in standings), Captain Clairfoyant (6th and 4th), and Peanuts (7th and 5th).

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

No new entries this week.

### Here's a look at the **points trendline** for each team.

```{r echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  geom_smooth(method="glm")+
  facet_wrap(~fullname)
```

Almost everyone besides the Sophomores were either the same or lower this week compared to last. Bye weeks and injuries will do that.

### If the season ended today...

Our playoff teams would be Erin/Trav, Richard, Robbie, and Brian. Our last place finisher would be Jacob. On the edge, the Peanuts lose out on the last playoff spot by tiebreaker/points. The Hobbits are one game out, and both the Sharks and Jaheims are two games back.

### Next week's preview

```{r,echo=FALSE}
nextweek1<-nextweek %>% select(away_team:range) %>%
  mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
         range=abs(away_points-home_points)) %>%
  mutate(Favored=if_else(away_points>home_points,
                         paste(away_team," (+",round(range,2),")",sep=""),
                         paste(home_team," (+",round(range,2),")",sep=""))) %>%
  select(-range)
names(nextweek1)<-c("Away team","Last 3 wks avg (away)","Home team","Last 3 wks avg (home)",
                   "Line")
kable(nextweek1)
```

It's a rematch next week between the Peanuts and Sophomores. I beat Erin and Trav last time around, but the numbers are not looking good this week. Past champions Brian and Robbie face off. The Hobbits and Gophers battle for the below ground title, and Jacob tries to get back on track against Sarah. Lastly, the closest game on paper this week is Richard vs. Evan.

Good luck, y'all! (And remember to check your byes!)
