---
title: 'PCFL 2021: Week 5 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(lubridate)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) < today()) %>%
  filter(mdy(Date)==max(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/leaguesched.csv")
team_list<-read_csv("data/teaminfo1.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))
nextweek<-read_csv(paste("data/nextweek_wk",week_sel,".csv",sep=""))
```

### Last week's games

```{r, echo=FALSE}
kable(last_week %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints))
```

And then there were none. Our last undefeated, The Sophomores, fell to my mighty Peanuts this week, despite putting up a respectable 132 points. Any given Sunday, y'all.

In other action, Brian' Captain Clairvoyant rebounded for a win this week against Sarah's Southern Sharks. Robby's Team Sasquatch clobbered Evan's Jumpin Jaheims, and Scott's Hobbits dug out the Gophers. Lastly, in a matchup for the Pages, The Pigskin on the Gridiron best the GOAT. 

#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Justin Herbert got my game ball this week, though Lamar Jackson's late comeback almost gave him the top spot (and made my game a little too close for comfort). In non-QB play, Mark Andrews scored 36 points on my bench (I went to bed in the *third quarter* and he only had around 8 points). A bunch of wide receivers topped 30, and Derrick Henry was the top RB.

#### Best addition and top bench
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

Dawson Knox was my starting TE this week and did admirably. Team Sasquatch also had a couple of nice pickups.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

A high scoring week! My bench nearly topped 100, but Brian, Sarah, and Christine weren't too far behind.

### League standings and season stats
Here's a look at the current standings.

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Pigskin on the Gridiron (by just 1.4 points over The Sophomores) 
* D-FENCE (least points allowed): Georgia Peanuts *_new_*
* Tough luck (points rank - playoff rank): Team Sasquatch AND Middle Earth Hangry Hobbits--third and fourth in points, but only sixth and seventh in the rankings.
* Lucky ducks (playoff rank - points rank): The Georgia Peanuts--third in playoff rankings but seventh in points

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

The Peanuts are on top! Just 0.35 points more than the Sophomores last week. Three teams, including Robby last week, sitting at 149 points.

### Here's a look at the **points trendline** for each team.

```{r echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```

Team Sasquatch and I are both headed up. Brian had a nice rebound week. 

### If the season ended today...

Our playoff teams would be Richard, Erin/Trav,Evan, me, and Brian. Our last place finisher would be Jacob.

### Next week's preview

```{r,echo=FALSE}
nextweek1<-nextweek %>% select(away_team:range) %>%
  mutate(Favored=if_else(away_points>home_points,
                         paste(away_team," (+",round(range,2),")",sep=""),
                         paste(home_team," (+",round(range,2),")",sep=""))) %>%
  select(-range)
names(nextweek1)<-c("Away team","Last 3 wks (away)","Home team","Last 3 wks (home)",
                   "Line")
kable(nextweek1)
```

The closest game of the week looks to be the Hobbits and Sasquatch, with a slight edge to Scott's team. The biggest mismatch pits the GOAT and Gophers, with Jacob heavily favored. 

Good luck, y'all!
