---
title: '**PCFL 2022: Week 4 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()


week_sel<-4

source("scripts/league_data.R")

```

Week 3 is in the books. How'd it go?

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Last week's game of the week was Jacob vs. Robbie, and it was a nail biter! Robbie edged out Jacob by just over 6 points, with plenty of points scored on both sides.

The mismatch of the week was Scott and Sarah, and as was predicted, it wasn't a close game. 10th seed Sarah blew our top scoring Hobbits away, in yet another case of matchup back luck for Scott.

In other games, Erin/Trav edged out Richard, Crissy continued her strong start against me, and Evan stayed unbeaten with a win against Brian.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Lots of running backs this week! Josh Jacobs and Miles Sanders are definitely not the usual suspects, and Russell Wilson had been off to a rough start. Team Sasquatch and the Jumpin' Jaheims both had some nice performances this week.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott's really kicking himself for leaving T.J. Hockenson on his bench. And check out the high flying 49ers defense on Jacob's squad.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Hobbits leading the pack this week.

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott's starting to pull away with this one, with Crissy and Jacob neck and neck behind him.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Nice work, Team Sasquatch and Southern Sharks. 

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}

ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))

# actual_rank<-actualpoints %>% 
#          group_by(Week) %>%
#          mutate(`Optimization rate`=as.numeric(str_replace(`Optimization rate`,"%","")),
#                 Week=paste("Week ",as.character(Week),sep=""),
#                 Rank=row_number()) %>%
#   arrange(-Rank)
# 
# ggplot(actual_rank,
#        aes(x=Rank,y=`Optimization rate`,fill=`PCFL Team`)) +
#   geom_bar(stat="identity",position="dodge") + 
#   xlab("")+
#   scale_fill_brewer(palette="Paired")+
#   theme_minimal()+
#   theme(axis.ticks.x=element_blank(),
#         axis.text.x=element_blank(),
#         text=element_text(family="Source Sans Pro"),
#         strip.text.x = element_text(size = 12,family="Source Sans Pro Semibold"))+
#   facet_wrap(~`Week`)
```

We'll see what happens as we get into bye weeks, but Evan's definitely having a nice season both in actual and possible points.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Very nice running back pickup for Sarah.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.


```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott's week 1 still is our top performance this season, but both Sarah and Evan got into the top 5 this week.

```{r eval=FALSE, echo=FALSE, message=FALSE}
#Lastly, here's a look at the **points trendline** for each team.

# teamtrend<-results %>%
#   select(awayteam,awaypoints,week) %>%
#   rename(teamId=awayteam,
#          points=awaypoints) %>%
#   bind_rows(results %>%
#               select(hometeam,homepoints,week) %>%
#               rename(teamId=hometeam,
#                      points=homepoints)) %>%
#   mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
#   left_join(team_list %>%
#               select(teamId,fullname))
# 
# ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
#   geom_line()+
#   geom_point(col="red")+
#   #geom_smooth()+
#   facet_wrap(~fullname)
```


## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Evan remains atop the leader board. Both he and Robbie remain unbeaten, but Evan's done a bit better in scoring to take a lead in team points. On the other end, it's a rebuilding year for Pigskin on the Gridiron, who has only one top 5 performance (but no wins) to boast about.


### If the season ended today...

Current playoff teams (ESPN): Evan and Crissy as division winners, Robbie and Jacob as wildcards

Current playoff teams (Team points): Evan, Robbie, Jacob, and Scott

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

There can only be one unbeaten team, and this week's featured matchup between Robbie and Evan will determine which owner will carry that title. Meanwhile, Scott tries to get back in the win column against the resurgent Gophers. Two family matchups the week: Richard vs. Jacob in the Battle of the Pages and me vs. Erin/Trav. Lastly, Sarah tries to keep the wins going against Brian.

Good luck, y'all!