---
title: '**PCFL 2023: Week 10 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-10

source("scripts/league_data.R")

```

Week 10 is a wrap!

The bye weeks are still ongoing, y'all. Don't be like [team redacted] who left their QB spot open this week.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Top scorer this week was Richard with 138 points! Sarah not far behind with 137. Brian brought up the rear with, well, about half that.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

A couple of benched quarterbacks (Howell and Purdy) and then QBs and WRs otherwise.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Evan's creeping up on my first place Peanuts!

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Erin/Trav, Jacob, and Brian all with points left on the bench this week.

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>%
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

### Point distribution by position

Here's a breakdown of point contribution by position by team so far this season. 

```{r, echo=FALSE}
ggplot(starters_pct,aes(y=points_pct,
                        x=franchise_name,
                        fill=franchise_name))+
  geom_bar(stat='identity')+
  ylab("% of points")+xlab("")+
  facet_wrap(~lineup_slot)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
   labs(fill = "Franchise name")
```

Fun facts: 

* The Seniors have gotten 29% of their points from the RB position. The Gophers have the least at 17%.
* Brian has STILL gotten just **29 TOTAL POINTS** from his DST position ALL SEASON. I'm the leader with 112, but Evan is next to last with 52 points--almost double Brian's total.
* Of the five top scoring positions in the league, 3 are WR (led by me with 334) and 2 are RB (led by Erin/Trav with 310). The lowest scoring position group is Brian's DST.

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Check out Russell Wilson. And I let go of Jaylen Warren maybe too soon.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

No changes this week.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott and I top the standings, though I win the points tiebreaker by 1.5.

### If the season ended today...

Playoffs currently stand as me, Scott, Sarah, and Robbie. 

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It's another #1 and #2 this week: me vs. Scott. Robbie vs. Richard is also a matchup of two hot teams. 

Good luck, y'all!