---
title: "**PCFL 2025: Week 10 wrap-up**"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    theme: united
  github_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
#library(hrbrthemes)
library(showtext)

setwd(here::here())

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()
week_sel=10

source("scripts/league_data.R")

```

It's week 11, y'all. That means we're now 2/3 of the way through the regular season. It's gone so fast!! 

I'm also sorry to have missed last week's update. I was on the road to Albuquerque, which was great. But I missed checking in with everyone.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Kind of a low scoring week, but the Jaheims (Evan) and Hobbits (Scott) had good showings.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Sharks best hope that Jonathan Taylor's ACLs are strong as steel. Best first round pick.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=`PCFL Team`))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

 Here's the season's bench standings:

```{r,echo=FALSE}
 kable(starter_benchteam_all %>%
         arrange(-`Bench points`) %>%
 rename(Team=name))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It's our two newest members (Ted and Will) leading the pack here.

### Best pick-ups
There were `r nrow(activity_info)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(activity_info %>% arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Waiver masters

I've tallied the players picked up by each team since the draft and the points they've contributed as starters. Here's where those stand.

```{r,echo=FALSE}
kable(roster_pickup %>%
        select(-abbrev) %>%
        rename(Team=name,Points=draftpoints,
               Transactions=draft_num) %>%
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

This is a tight one still, but me and Robby are neck and neck at the top here. I've also added the number of transactions to this list. The Gophers have been, well, a little dormant.

### Recapping the draft
Here's the amount of points drafted players have contributed to each team as starters.

```{r,echo=FALSE}
kable(roster_draft %>% 
         select(-abbrev) %>%
        rename(Team=name,Points=draftpoints) %>% 
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Sharks are WELL on top here. Of her 1,055 points, 259 have come from Jonathan Taylor.

### Best team performances 

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        arrange(-Score))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Don't look now, but Pigskin (Richard) is having a sneaky good season.

## Looking ahead

### League standings

Our league standings are a little unusual. We rank teams based on points, kinda like hockey. There are two ways to get points:

* Win your weekly matchup (1 point)
* Finish in the top six point scorers (1 point)

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

It's Sarah and Ted neck and neck for the lead here.

### If the season ended today...

Our playoff teams would be the Sharks, Henry's, Broncos, and Pigskin on the Gridiron. 

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Of note--the Toilet Bowl Trophy has an early preview with the Gophers vs. Clairvoyant matchup. Pigskin vs. Henry's is the top game of the week.

Good luck, y'all!