---
title: 'PCFL: Week 5 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
library(httr)
library(tidyverse)
library(lubridate)
library(knitr)

#ReadData
year<-2020
league<-1403922
week_sel<-6

url_match<-paste("https://fantasy.espn.com/apis/v3/games/ffl/seasons/",
          year,"/segments/0/leagues/",league,"?view=mMatchup",sep="")
match_raw<-GET(url_match)

MatchRaw <- rawToChar(match_raw$content)
Match <- jsonlite::fromJSON(MatchRaw)

# url_teams<-paste("https://fantasy.espn.com/apis/v3/games/ffl/seasons/",
#             year,"/segments/0/leagues/",league,sep="")
# teams_raw<-GET(url_teams)
# TeamsRaw <- rawToChar(teams_raw$content)
# Teams <- jsonlite::fromJSON(TeamsRaw)

url_standing<-paste("https://fantasy.espn.com/apis/v3/games/ffl/seasons/",
          year,"/segments/0/leagues/",league,"?view=mStandings",sep="")
standing_raw<-GET(url_match)

StandingRaw <- rawToChar(standing_raw$content)
standings <- jsonlite::fromJSON(StandingRaw)

# url_sched<-paste("https://fantasy.espn.com/apis/v3/games/ffl/seasons/",
#           year,"/segments/0/leagues/",league,"?view=mSchedule",sep="")
# sched_raw<-GET(url_sched)
# 
# SchedRaw <- rawToChar(sched_raw$content)
# sched <- jsonlite::fromJSON(SchedRaw)

# schedule<-tibble(
#   week=Match$schedule$matchupPeriodId,
#   away_id=Match$schedule$away$teamId,
#   home_id=Match$schedule$home$teamId
# )
# write_csv(schedule,"data/league_schedule.csv")

schedule<-read_csv("data/league_schedule.csv")

# 
# team_list<-Teams$teams %>%
#   mutate(teamid=row_number(),
#          fullname=paste(location,nickname))
# write_csv(team_list %>%
#             select(-owners),"league_roster.csv")
team_list<-read_csv("data/league_roster.csv")

away<-tibble(
  teamId=standings$schedule$away$teamId,
  totalPoints=standings$schedule$away$totalPoints) %>%
  filter(totalPoints>0) %>%
  #select(-gamesPlayed) %>%
  rename(awayteam=teamId,awaypoints=totalPoints)
home<-tibble(
  teamId=standings$schedule$home$teamId,
  totalPoints=standings$schedule$home$totalPoints)  %>%
  filter(totalPoints>0) %>%
  #select(-gamesPlayed) %>%
  rename(hometeam=teamId,homepoints=totalPoints)
results<-bind_cols(away,home) %>%
  mutate(away_result=if_else(awaypoints>homepoints,"W","L"),
         home_result=if_else(homepoints>awaypoints,"W","L"),
         week=ceiling(row_number()/5))

#Create standings
names<-c("teamId","points_scored","points_allowed","result","week")
away_sel<-results %>%
  select(awayteam,awaypoints,homepoints,away_result,week)
names(away_sel)<-names

home_sel<-results %>%
  select(hometeam,homepoints,awaypoints,home_result,week)
names(home_sel)<-names

stand_tbl1<-bind_rows(away_sel,home_sel) %>%
  group_by(teamId) %>%
  summarise(points_scored=sum(points_scored),
            points_allowed=sum(points_allowed))
stand_tbl<-bind_rows(away_sel,home_sel) %>%
  count(teamId,result) %>% 
  left_join(team_list %>% select(teamId,fullname,division)) %>%
  pivot_wider(names_from=result,
              values_from=n,
              values_fill=0) %>%
  left_join(stand_tbl1) %>%
  select(fullname,division,W,L,points_scored,points_allowed) %>%
  arrange(-points_scored) %>%
  mutate(points_rank=1:n()) %>%
  arrange(-W,-points_scored) %>% 
  mutate(playoff_rank = 1:n())


#Last week's games
player_extract<-function(team_slot){
  df<-Match$teams$roster$entries[[team_slot]]
  add_date<-as.Date(as.POSIXct(df$acquisitionDate/1000, origin="1970-01-01"))
  name<-df$playerPoolEntry$player$fullName
  points<-df$playerPoolEntry$appliedStatTotal
  slot<-df$lineupSlotId
  
  tibble(add_date,name,points,slot) %>%
    mutate(bench=if_else(slot<20,0,1),
           rowid=team_slot)
}
players<-map_df(1:10,player_extract) %>%
  left_join(team_list)
#write_csv(players,"data/players_wk3.csv")

benchpoints<-players %>%
  group_by(abbrev,bench) %>%
  summarise(points=sum(points)) %>%
  filter(bench==1) %>%
  left_join(team_list) %>%
  ungroup() %>%
  select(fullname,points)

recent_adds<-players %>%
  mutate(stay=time_length(interval(start=add_date,end=today()),"day")) %>%
  filter(stay<7)

nextweek_long<-schedule %>%
  filter(week==week_sel) %>%
  mutate(gameid=row_number()) %>%
  pivot_longer(away_id:home_id,
               names_to="awayhome",
               values_to="teamId") %>%
  left_join(team_list %>% 
              select(teamId,fullname)) %>%
  left_join(stand_tbl %>%
              select(fullname,points_scored)) %>%
  select(-teamId) 
  
nextweek<-nextweek_long %>%
  filter(awayhome=="away_id") %>%
  rename(away_team=fullname,
         away_points=points_scored) %>%
  left_join(nextweek_long %>%
              filter(awayhome=="home_id") %>%
              select(-awayhome) %>%
              rename(home_team=fullname,
                     home_points=points_scored)) %>%
  mutate(range=abs(away_points-home_points)) %>%
  select(-gameid,-awayhome) 

#Last week's games
last_week<-results %>%
  filter(week==max(week)) %>%
  select(-away_result:-week) %>%
  left_join(team_list %>%
              select(teamId,fullname) %>%
              rename(awayteam=teamId)) %>%
  rename(away_team=fullname) %>%
  left_join(team_list %>%
              select(teamId,fullname) %>%
              rename(hometeam=teamId)) %>%
    rename(home_team=fullname) %>%
  select(away_team,awaypoints,home_team,homepoints)
```

### Last week's games

```{r, echo=FALSE}
kable(last_week)
```

Congrats to Evan for getting his first win! He didn't have a great scoring week, but it was a big enough boat to down Sarah's Sharks. Team Sasquatch (Robbie) also managed to stomp on the First Timers' hot streak. And the Hangry Hobbits were this week's point leaders. Much rejoicing reported from the Shire.

#### Best performing players

Here's last week's **10 best performing players.** The bench variable shows whether they got left on the bench or not.

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname,bench),10,points) %>%
        arrange(-points))
```

Quarterback heavy numbers here--the top four players were all under center last week, and QBs were 6 of the top 10. The Ravens' defense powered the Hobbits' win this week with 25 (!) points. Mike Davis' days as a starter for me may be numbered, but he's done well stepping in when injury gave an opportunity.

#### Best addition and worst starters
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        arrange(-points))
```

Team Sasquatch had three great adds this week, but Justin Herbert also did great for Evan.


Who should have been **left on the bench** this week--the lowest points scored by starters?

```{r,echo=FALSE}
kable(top_n(players %>% 
              filter(bench==0) %>%
              select(name,points,fullname),5,-points) %>%
        arrange(points))
```

Start a defense at your peril. The Chiefs were having a good run, but came back to earth this week (even if Brian still pulled out the W). The 49ers also had an off week.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points))
```

Hangry Hobbits had points to spare! 95 points for them. It appears that Sarah could have used some points off the bench.

### League standings and season stats
Here's a look at our current standings

```{r, echo=FALSE}
kable(stand_tbl)
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): Captain Clairvoyant
* D-FENCE (least points allowed): KC Gophers
* Tough luck (points rank - playoff rank): The First Timers
* Lucky ducks (playoff rank - points rank): KC Gophers

Here's a list of the **top five scoring performances** so far this season.

```{r, include=FALSE}
toppoints<-bind_rows(away_sel,home_sel) %>%
  left_join(team_list) %>%
  select(fullname,week,points_scored,result) %>%
  top_n(5,points_scored) %>%
  arrange(-points_scored) 
```
```{r, echo=FALSE}
kable(toppoints)
```

Scott's hot week puts the Hobbits in as our new #3.

Lastly, here's a look at the **points trendline** for each team.

```{r, echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=as.character(week)) %>%
  left_join(team_list %>%
              select(teamId,fullname))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  #geom_smooth()+
  facet_wrap(~fullname)
```


## Next week's games

Here's a quick summary of next week's matchups:

```{r,echo=FALSE}
kable(nextweek)
```

It's a Stertz sister matchup between the First Timers and Sharks this week, so sparks will surely fly. KC Gophers will have to dig deep to see if their luck holds out against Captain Clairvoyant. The closest matchup of the week is me against Scott--we'll see how hungry those hobbits really are. Good luck all!
