---
title: '**PCFL 2023: Week 1 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-1

source("scripts/league_data.R")

```

Hey all! Welcome back for another season.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It was a record low week for offenses across the fantasy world, and it was no exception here. Four teams failed to get over 80 points. Richard was our first weekly top scorer.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Cowboys defense was otherwordly last week. The rest of the names at the top of the list are no surprise.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```


```{r,echo=FALSE}
# Here's the season's bench standings:
# 
# kable(starter_benchteam_all %>% 
#         arrange(-`Bench points`) %>%
#   rename(Team=franchise_name))%>%
#   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```


### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

A whole lotta folks left points on the bench.


```{r,echo=FALSE, include=FALSE}
# For the *whole season*, here's a table of actual points scored vs. optimized points given the roster. 
# 
# 
# kable(actualpoints_season %>%
#         pivot_wider(names_from=Type,values_from=Points) %>%
#         mutate(Optimization=paste(round(`Actual points`/`Optimized points`*100,0),
#                                           "%",sep="")) %>%
#         select(-rank) %>%
#         arrange(desc(Optimization)))   %>%
#   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
# 
# 
# # ggplot(actualpoints_season %>% 
# #          mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
# #        aes(x=Points,y=`PCFL Team`))+
# #   geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
# #   geom_point(aes(color=Type),size=3.1)+
# #   theme_minimal()+
# #   scale_color_manual(values=c( "#E69F00","#999999"))+
# #   theme(text=element_text(family="Source Sans Pro",size = 12))
```

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
# kable(newadds) %>%
#   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

[Coming soon]

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Yeah, it's week 1.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Still so, so early.

### If the season ended today...

Really? It's just week one. We'll come back to this.

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Stertzes of the Great North battle for supremacy in this week's matchup of Sharks vs Seniors among other matchups.

Good luck, y'all!