---
title: '**PCFL 2025: Week 3 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    theme: united
    css: |
      .tocify {
        width: 250px !important;
        border: 1px solid #ccc;
        border-radius: 5px;
      }
      .tocify-header {
        font-weight: bold;
        font-size: 14px;
      }
      .tocify-subheader {
        font-size: 12px;
        padding-left: 15px;
      }
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(showtext)

setwd(here::here())

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()
week_sel=3

source("scripts/league_data.R")

```

Lots of travel last week, so the weekly update didn't make it out. But here's where we stand for week 3.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Hangry Hobbits (Scott) had a great week, and Team Sasquatch (Robbie) definitely did not. 

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Vikings defense, lol.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=`PCFL Team`))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

 Here's the season's bench standings:

```{r,echo=FALSE}
 kable(starter_benchteam_all %>%
         arrange(-`Bench points`) %>%
 rename(Team=name))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

A very close race!

### Best pick-ups
There were `r nrow(activity_info)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
 kable(activity_info %>% arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best team performances 

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
 kable(arrange(toppoints,-Score))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

## Looking ahead

### League standings

For new folks, our league standings are a little unusual. We rank teams based on points, kinda like hockey. There are two ways to get points:

* Win your weekly matchup (1 point)
* Finish in the top six point scorers (1 point)

So this week, Evan got two points because he won and had a lot of points. But Robbie (Sasquatch) only got one point. He was in the top six point scorers, but he lost his game.

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

### If the season ended today...

Our playoff teams would be the Broncos, Sharks, Jaheims, and the Henry's (using a tiebreaker of total points scored). Two of our newbies in the top 4!

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Good luck, y'all!