---
title: '**PCFL 2023: Week 1 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-2

source("scripts/league_data.R")

```

Week 2 is in the books!

Commissioner's reminder at the outset: last year we moved to a different system of ranking for teams. Each week, your team will receive up to two points. One is awarded for a win, and the other is awarded if you finish in the top 5 in scoring. 

This is to recognize that you as an owner have no control over your opponent's scoring, and so it provides a little bonus for what you can control, which is scoring points. This week, for example, Sarah took the L, but was fourth in scoring. So she still gets some credit for that. 

Side note #2: Be a little kinder to Richard this week. He was the first one eliminated from the Pan-Continental Guillotine Football League.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The less said about Scotts perfomance the better. Richard, Erin/Trav, and Sarah also had nice weeks.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Just as I planned, Daniel Jones is the foundation of my fantasy success. Richard got some nice wide receiver play.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Fun fact--according to this readout, 7/10 teams had their top scorer on the bench last week.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Two teams topped 100 bench points last week. Impressive work, Sarah and Evan!

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Sarah, as expected, has the early lead for bench points, but I'm not far behind.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a table of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE, include=FALSE}


kable(actualpoints_season %>%
        pivot_wider(names_from=Type,values_from=Points) %>%
        mutate(Optimization=paste(round(`Actual points`/`Optimized points`*100,0),
                                          "%",sep="")) %>%
        select(-rank) %>%
        arrange(desc(Optimization)))   %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

# 
ggplot(actualpoints_season %>%
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Kyren Williams and Puka Nacua were both nice pickups last week.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott may keep that top spot for awhile, but Richard and Erin/Trav have put together impressive starts.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Still so, so early. But Brian and I need to get on track this week.

### If the season ended today...

Really? It's just week two. We'll come back to this.

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It's a divided household for Sarah and me in a matchup of the winless. 

Good luck, y'all!