---
title: "**PCFL 2025: Week 11 wrap-up**"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    theme: united
  github_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
#library(hrbrthemes)
library(showtext)

setwd(here::here())

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()
week_sel=11

source("scripts/league_data.R")

```

Getting down to crunch time! Let's see where we check in with just four weeks left.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Call us Middle Earth, because this was the Hobbits' week to rule. The Sharks had to settle with coming in second.

## Best performances

### Best players overall
Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(starters,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Ouch--Sean Tucker with 33 on the bench for Team Sasquatch.

<!-- ### Best players per team -->
<!-- Here's last week's top players **on each team.** -->

<!-- ```{r,echo=FALSE} -->
<!-- kable(starter_team)%>% -->
<!--   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left") -->
<!-- ``` -->

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=`PCFL Team`))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Here's the season's bench standings:

```{r,echo=FALSE}
 kable(starter_benchteam_all %>%
         arrange(-`Bench points`) %>%
 rename(Team=name))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Our two newest members (Ted and Will) continue setting the pace here.

### Best pick-ups
There were `r nrow(activity_info)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(activity_info %>% arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Dortch is a great football name.

### Waiver masters

I've tallied the players picked up by each team since the draft and the points they've contributed as starters. Here's where those stand.

```{r,echo=FALSE}
kable(roster_pickup %>%
        select(-abbrev) %>%
        rename(Team=name,Points=draftpoints,
               Transactions=draft_num) %>%
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Robbie has taken the lead here, but this is really just about volume. He's averaged 10 points per added player, but I'm at 10.5. So there.

### Recapping the draft
Here's the amount of points drafted players have contributed to each team as starters.

```{r,echo=FALSE}
kable(roster_draft %>% 
         select(-abbrev) %>%
        rename(Team=name,Points=draftpoints) %>% 
        arrange(-Points)) %>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best team performances 

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        arrange(-Score))%>%
   kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

No changes to see here.

## Looking ahead

### League standings

Our league standings are a little unusual. We rank teams based on points, kinda like hockey. There are two ways to get points:

* Win your weekly matchup (1 point)
* Finish in the top six point scorers (1 point)

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

At this point, Sarah and Ted are basically locks for the playoffs. There's five teams with 12-14 points, so the last two slots are really up for grabs.

### If the season ended today...

Our playoff teams would be the Sharks, Henry's, Broncos, and GOAT.

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Good luck, y'all!