---
title: 'PCFL 2021: Week 12 wrap-up'
output: html_document
editor_options: 
  chunk_output_type: console
---

Countdown to the playoffs! Only **THREE** weeks to go.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(lubridate)
library(purrr)

weeks<-read_csv("data/week_dates.csv") %>%
  filter(mdy(Date) < today()) %>%
  filter(mdy(Date)==max(mdy(Date)))
week_sel<-weeks$Week


#knitr::opts_knit$set(root.dir = "C:/Users/jshannon/Dropbox/Jschool/Other/pcfl2020")
schedule<-read_csv("data/leaguesched.csv")
team_list<-read_csv("data/teaminfo1.csv")
players<-read_csv(paste("data/players_wk",week_sel,".csv",sep=""))
recent_adds<-read_csv(paste("data/recent_adds_wk",week_sel,".csv",sep=""))
last_week<-read_csv(paste("data/wk",week_sel,".csv",sep=""))
benchpoints<-read_csv(paste("data/benchpoints_wk",week_sel,".csv",sep=""))
stand_tbl<-read_csv(paste("data/stand_tbl_wk",week_sel,".csv",sep=""))
toppoints<-read_csv(paste("data/toppoints_wk",week_sel,".csv",sep=""))
results<-read_csv(paste("data/results_wk",week_sel,".csv",sep=""))
nextweek<-read_csv(paste("data/nextweek_wk",week_sel,".csv",sep=""))

lastweek_line<-read_csv(paste("data/nextweek_wk",week_sel-1,".csv",sep="")) %>%
  select(away_team:range) %>%
  mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
         range=abs(away_points-home_points)) %>%
  mutate(Favored=if_else(away_points>home_points,
                         paste(away_team," (+",round(range,2),")",sep=""),
                         paste(home_team," (+",round(range,2),")",sep=""))) %>%
  select(-range,-away_points,-home_points)

benchpoints_files<-paste("data/",list.files(path = "data",pattern="benchpoints"),sep="")
benchpoints_sum<-map_df(benchpoints_files,read_csv) %>%
  group_by(fullname) %>%
  summarise(points=sum(points))
```

### Last week's games

```{r, echo=FALSE, message=FALSE}
kable(last_week %>%
        left_join(lastweek_line) %>%
        rename(Away=away_team,
               `Away points`=awaypoints,
               Home=home_team,
               `Home points`=homepoints,
               `Predicted result`=Favored))
```

Last week's game of the week was Gophers vs. Sophomores, with the latter favored by 46(!) points. It wasn't a nail biter, but the Sophomore's winning margin of 13 seems much slimmer when considering that the Gophers had two starters on bye. Could have been an upset! 

Richard and Robbie were the two high scorers this week. Richard put a damper on Scott's playoff hopes, and Brian beat out a strong performance by Jacob. On the other side of things, my Peanuts had the second lowest point total this week but still notched a win! Thanks to the (newly co-managed) Sharks for making it possible. Lastly, Evan eked out a victory against Brian in the closest contest of the week.

#### Best performing players

Here's last week's **10 best performing players.** 

```{r,echo=FALSE}
kable(top_n(players %>% 
              select(name,points,fullname),10,points) %>%
        rename(Player=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

A great week for running backs: Leonard Fournette and Joe Mixon both did well. And after three teams, something finally has clicked for Cordarrelle Patterson in Atlanta.

#### Best addition and top bench
There were `r nrow(recent_adds)` players added last week. Which was the **best new addition**?

```{r echo=FALSE}
kable(recent_adds %>% 
        select(add_date,name,points,fullname) %>%
        rename(`Date added`=add_date,
               Name=name,
               Points=points,
               Team=fullname) %>%
        arrange(-Points))
```

I considered OBJ for a bit, but figured the glory days were behind him. Kudos to Robbie for giving him a chance. Dontrell Hilliard also did a nice job as the most recent RB to try to replace Derrick Henry in Tennessee.

Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(benchpoints %>% arrange(-points)%>%
  rename(Team=fullname,Points=points)) 
```

Richard had a strong victory this week! Sarah was shockingly seventh...

Who has the most bench points for the _season_? Here's the current standings:

```{r,echo=FALSE}
kable(benchpoints_sum %>% 
        arrange(-points) %>%
        rename(`Team name`=fullname,`Total bench points`=points)) 

```

Sarah remains in the lead, but Scott's slowly creeping up on that top spot.

### League standings and season stats
Here's a look at the current standings.

```{r, echo=FALSE}
kable(stand_tbl %>%
        rename(Team=fullname,
               Division=division,
               `Points scored`=points_scored,
               `Points allowed`=points_allowed,
               `Points rank`=points_rank,
               `Playoff rank`=playoff_rank))
```

Here's our current awards leaders from these standings:

* Yellow shirt (most points): The Sophomores
* D-FENCE (least points allowed): Captain Clairvoyant (by just .29 points over me!)
* Tough luck (points rank - playoff rank): Southern Sharks--fifth in points but eighth in the rankings
* Lucky ducks (playoff rank - points rank): Jumpin' Jaheims *new*--eighth in points but sixth in the rankings

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(toppoints %>%
        rename(Team=fullname,
               Week=week,
               `Points scored`=points_scored,
               Result=result))
```

Nothing to see here.

### Here's a look at the **points trendline** for each team.

```{r echo=FALSE, message=FALSE}
teamtrend<-results %>%
  select(awayteam,awaypoints,week) %>%
  rename(teamId=awayteam,
         points=awaypoints) %>%
  bind_rows(results %>%
              select(hometeam,homepoints,week) %>%
              rename(teamId=hometeam,
                     points=homepoints)) %>%
  mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
  left_join(team_list %>%
              select(teamId,fullname)) %>%
  group_by(week) %>%
  mutate(weekmdn=median(points))

ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
  geom_line()+
  geom_point(col="red")+
  geom_smooth(method="glm")+
  facet_wrap(~fullname)
```

Y'all can try to make sense of this at this point. A lot of ups and downs in recent weeks.

Here's the points trend for *_all_* teams by week

```{r, echo=FALSE}
ggplot(teamtrend)+
 geom_boxplot(alpha=0.3,aes(x=week,y=points))+
 geom_point(alpha=0.8,aes(x=week,y=points,color=fullname))+
 labs(color='Team') 
```

Another down week this week--third lowest median score of the season.

### If the season ended today...

Things are just coming into focus. Erin and Trav pretty much have a lock on a playoff spot. They'd have to lose out AND Richard or I would have to win out AND score about 100 more points over just three weeks. Not gonna happen. The other teams today would be Robbie, Brian and Richard. But I'm tied for that last playoff spot by record, and Evan is just one game out with three to go. 

### Next week's preview

```{r,echo=FALSE}
nextweek1<-nextweek %>% select(away_team:range) %>%
  mutate(away_points=round(away_points/3,2),home_points=round(home_points/3,2),
         range=abs(away_points-home_points)) %>%
  mutate(Favored=if_else(away_points>home_points,
                         paste(away_team," (+",round(range,2),")",sep=""),
                         paste(home_team," (+",round(range,2),")",sep=""))) %>%
  select(-range)
names(nextweek1)<-c("Away team","Last 3 wks avg (away)","Home team","Last 3 wks avg (home)",
                   "Line")
kable(nextweek1)
```

This week's game of the week is Brian vs. Erin and Trav in a battle of playoff contenders. Brian needs a win to stay in the mix, with the Sophomores can clinch their first playoff appearance with a victory. Sarah and Scott are both long shots for the playoffs, but their game this week could end one of their seasons. Another battle for the Pages this week, with Richard facing Jacob. In other action, Robbie faces Evan, and I'm up against Christine.

Good luck, y'all! (And remember to check your byes!)
