---
title: '**PCFL 2023: Week 9 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-9

source("scripts/league_data.R")

```

Week 7 is a wrap!

The bye weeks are ongoing y'all. Also, this week's Sunday Europe game is Colts-Patriots, kicking off at 9:30 ET. Check your lineups!!

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Top scorer this week was Jacob's GOAT with 122 points. Six of our ten teams scored between 86 and 90 points. #parity

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Check out the Chargers defense this week!

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I benched CJ Stroud, thinking his rookie mojo had run out. Then he scores 42. Sigh. Relately, Tank Dell scored nearly 30 on Robbie's bench.

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I've got a comfortable lead at this point. Evan and Robbie are the only ones within 100 points.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Robbie could have had a 151 point week! 

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>%
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

### Point distribution by position

Here's a breakdown of point contribution by position by team so far this season. 

```{r, echo=FALSE}
ggplot(starters_pct,aes(y=points_pct,
                        x=franchise_name,
                        fill=franchise_name))+
  geom_bar(stat='identity')+
  ylab("% of points")+xlab("")+
  facet_wrap(~lineup_slot)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
   labs(fill = "Franchise name")
```

Fun facts: 

* The GOAT is tops in percentage of points from the QB position (24%) but last in WR points (17%).
* Brian has now gotten **29 TOTAL POINTS** from his DST position ALL SEASON. The Chargers defense scored 26 LAST WEEK.
* The Gophers are the only team with 10% or more of points coming from their kicker.

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Team Sasquatch had a monster week last week. That one will be hard to top.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

And even with the loss last week, Robbie still sits as the number one seed going into week 10. Brian's got the lead for the toilet trophy.

### If the season ended today...

It's Robbie, me, Scott, and Erin/Trav right now. Sarah is tied with Erin on team points, but the Sharks have scored about 70 fewer points. 

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It's #1 and #2 this week as I take on Robbie. 

Good luck, y'all!