---
title: '**PCFL 2023: Week 4 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-4

source("scripts/league_data.R")

```

Week 4 is a wrap!

The bye weeks have arrived y'all. Check your lineups!!

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Peanuts finally won! (And some of you also did, too. Evan had an OK week.)

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Christian McCaffrey was the correct answer for the best first round choice, clearly. Nice job, Seniors. And check out rookie Anthony Richardson making the list.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Yay, Peanuts!

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Sarah's in second, but probably not for long.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>%
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

Seniors at the top for both actual and optimized points.

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The Seahawks defense was something!

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Scott still hanging tight at the top.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Seniors and Pigskin at the top, with the Sharks circling not far behind. Richard's the only 4-0 team left.

### If the season ended today...

Seniors, Pigskin, and Sharks would be in. Jumpin' Jaheims would win the tiebreaker for the last spot. But it's still early.

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

We'll see if Jacob can end his dad's undefeated streak.

Good luck, y'all!