---
title: '**PCFL 2023: Week 11 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-11

source("scripts/league_data.R")

```

Week 11 is a wrap. Just four weeks left in the regular season!

While this hasn't been Brian's best PCFL season, you should keep him all in your thoughts and prayers this week. He's in the championship game for our guillotine league.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Kind of a low scoring week this week, but bye weeks will do that to you. Scott led the way with 115 points, and no one did especially poorly.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I still think Tank Dell is such a great football name, and the Texans are having a nice season overall.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I've got the end zone in sight! Just hope there's enough gas in the tank to get over the goal line.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Rough week for my Peanuts.

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}
ggplot(actualpoints_season %>%
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

The Hobbits inching into first on points scored, and with a very efficient use of players.

### Point distribution by position

Here's a breakdown of point contribution by position by team so far this season. 

```{r, echo=FALSE}
ggplot(starters_pct,aes(y=points_pct,
                        x=franchise_name,
                        fill=franchise_name))+
  geom_bar(stat='identity')+
  ylab("% of points")+xlab("")+
  facet_wrap(~lineup_slot)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
   labs(fill = "Franchise name")
```

Fun facts for the week: 

* With a solid week, Brian's DST is finally up over 40 points. By comparison, Richard's first with *133*.
* In contrast, Brian's TE group has scored 135 points, second only to Jacob (138). Here, Richard is LAST with just 62.
* WRs still are the highest scoring bunch, 4 out of the 5 top scoring units. The leader here is Robbie (355).

### Best pick-ups
There were `r nrow(newadds)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

A couple of nice RB pickups, but otherwise a little underwhelming.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

No changes this week, and really not much since week 4.

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott's taken control! There's also a logjam for 4th-6th place between Robbie, Erin/Trav, and Sarah.

### If the season ended today...

Playoffs currently stand as Scott, me, Richard, and Robbie (tiebreaker is total points). 

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

We'll see if Richard can knock Scott out of first, and Jacob has the task of dethroning Robbie this week.

Good luck, y'all!