---
title: '**PCFL 2022: Week 6 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()


week_sel<-6

source("scripts/league_data.R")

```

Apologies for no recap last week (and the short one this week). The commissioner's been on research trips around the country and it's cut into his analysis time.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The byes have begun, and with them, a drop in our scoring. The top matchup last week was the Hobbits vs. the Sasquatch, and Robbie has now dropped two in a row after a hot start. Crissy's Gophers also stayed hot, roasting Jacob's GOAT. Evan had a down week points wise, but still managed enough for the W over Erin and Trav. I bested Brian, and Richard got his first W.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Check out the tight ends! 

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Jacob got the top spot this week, followed by Crissy, me, and Robbie.

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott's dominant offense extends to his bench as well, while Brian, me, and Robbie are leaving it mostly on the field.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

```{r,echo=FALSE}

ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))

# actual_rank<-actualpoints %>% 
#          group_by(Week) %>%
#          mutate(`Optimization rate`=as.numeric(str_replace(`Optimization rate`,"%","")),
#                 Week=paste("Week ",as.character(Week),sep=""),
#                 Rank=row_number()) %>%
#   arrange(-Rank)
# 
# ggplot(actual_rank,
#        aes(x=Rank,y=`Optimization rate`,fill=`PCFL Team`)) +
#   geom_bar(stat="identity",position="dodge") + 
#   xlab("")+
#   scale_fill_brewer(palette="Paired")+
#   theme_minimal()+
#   theme(axis.ticks.x=element_blank(),
#         axis.text.x=element_blank(),
#         text=element_text(family="Source Sans Pro"),
#         strip.text.x = element_text(size = 12,family="Source Sans Pro Semibold"))+
#   facet_wrap(~`Week`)
```

Both Crissy and Erin/Trav have definitely left some points on the bench.

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

I was VERY happy to pick up Kenneth Walker for my meager RB room. Mike Gesicki also had a nice week for Crissy.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.


```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

No new additions here this week (and maybe for a bit with the byes).

```{r eval=FALSE, echo=FALSE, message=FALSE}
#Lastly, here's a look at the **points trendline** for each team.

# teamtrend<-results %>%
#   select(awayteam,awaypoints,week) %>%
#   rename(teamId=awayteam,
#          points=awaypoints) %>%
#   bind_rows(results %>%
#               select(hometeam,homepoints,week) %>%
#               rename(teamId=hometeam,
#                      points=homepoints)) %>%
#   mutate(week=factor(week,levels=c(1,2,3,4,5,6,7,8,9,10,11, 12,13,14))) %>%
#   left_join(team_list %>%
#               select(teamId,fullname))
# 
# ggplot(teamtrend,aes(x=week,y=points,group=fullname))+
#   geom_line()+
#   geom_point(col="red")+
#   #geom_smooth()+
#   facet_wrap(~fullname)
```


## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Evan's definitely on top when it comes to wins, two games ahead of Robbie and Crissy. Scott and Jacob share the runner up podium when it comes to team points, and Scott's still the overall points leader.

### If the season ended today...

Current playoff teams (ESPN): Evan and Crissy as division winners, Scott and Jacob as wildcards

Current playoff teams (Team points): Evan, Robbie, Jacob, and Scott

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Next week's game of the week is Scott vs. Jacob, as two playoff contenders try to keep pace with the league. But it's also worth keeping an eye on Evan vs. Sarah to see if the fantasy gods grant the upset and knock Evan from the ranks of the undefeated. Elsewhere, Richard tries to start a win streak against me, Robbie tries to get back in the win column vs. Erin/Trav, and Brian faces off against Crissy in two tightly matched teams.

Good luck, y'all!