---
title: '**PCFL 2022: Week 12 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-12

source("scripts/league_data.R")

```

Hey all! We've got just two weeks to go in the regular season.

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

It was a tough loss week last week: Richard lost by 1.46 points and Brian by just 0.76 points! On the other hand, the Sasquatch gobbled down the GOAT by 55.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters_10,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Josh Jacobs with the stand out week, and look at Kirk Cousins go for the Gophers.

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Nice work by Crissy this week.

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>% 
        arrange(-`Bench points`) %>%
  rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Evan's taken the lead here. Worth noting that our leading points scorers also have the highest scoring benches.

### Best optimized lineups
I compared the actual starting lineups for each team to the hypothetical _best_ starting lineup the owner could have started. The table below shows the actual points the team scored, the top score they could have had, and an "optimization" percentage that compares to the two.

```{r,echo=FALSE}
kable(actualpoints %>% 
        filter(Week==week_sel) %>% 
        select(-Week)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```


```{r,echo=FALSE, include=FALSE}
#For the *whole season*, here's a graph of actual points scored vs. optimized points given the roster. 

ggplot(actualpoints_season %>% 
         mutate(`PCFL Team` = fct_reorder(`PCFL Team`, desc(rank))),
       aes(x=Points,y=`PCFL Team`))+
  geom_line(aes(x=Points,y=`PCFL Team`,group=`PCFL Team`))+
  geom_point(aes(color=Type),size=3.1)+
  theme_minimal()+
  scale_color_manual(values=c( "#E69F00","#999999"))+
  theme(text=element_text(family="Source Sans Pro",size = 12))
```

### Best additions
There were `r nrow(newadds)` players added last week. Which was the **best new addition**?

```{r,echo=FALSE}
kable(newadds) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Not too much here, but a couple of good RB adds at the top of the list.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}

kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Robbie and Sarah dominating this list!

## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Scott and Evan are tops in the league, with Robbie in third. Sarah, Richard, and Brian are  fighting it for the toilet trophy.

### If the season ended today...

Here's our playoff picture  right now: 
* Division winners: Evan (17 points, Grits), and Scott (18 points, Hot Dish). 
* Wild cards: Robbie (14 points) and me (13 points)

The ESPN version at this point would be identical, as I'd have the tie-breaker over Criss and Erin/Trav based on total points.

### Next week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Crissy and I go head to head this week with that last playoff spot at stake, while Erin/Trav try to keep pace against Brian, who may well be tanking for the toilet trophy at this point. Evan vs. Robbie is another high scoring matchup to watch. This week's family match up is Richard vs. Jacob.

Good luck, y'all! (And check your byes!)