---
title: '**PCFL 2024: Week 4 wrap-up**'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: united
  github_document:
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
library(svglite)
library(kableExtra)
library(hrbrthemes)
library(extrafont)
library(showtext)

setwd(here::here())

#font_add_google("IBM Plex Sans", "ibm")
extrafont::loadfonts()

week_sel<-10

source("scripts/league_data.R")

```

Week 4 is a wrap! And here's the first real weekly update of the season

## Last week's games

```{r, echo=FALSE}
kable(lastweek_results)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Evan with a very strong week. The Gophers remain undefeated.

## Best performances

### Best players overall
Here's last week's **10 best performing starters.** 

```{r,echo=FALSE}
kable(top_n(starters,10,Points) %>%
        arrange(-Points))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best players per team
Here's last week's top players **on each team.**

```{r,echo=FALSE}
kable(starter_team)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

### Best bench
Who won the **best scoring bench** award last week?

```{r,echo=FALSE}
kable(starter_benchteam %>% 
        arrange(-`Bench points`) %>%
  rename(Team=`PCFL Team`))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Here's the season's bench standings:

```{r,echo=FALSE}
kable(starter_benchteam_all %>%
        arrange(-`Bench points`) %>%
rename(Team=franchise_name))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Richard is running away with this one early on.

### Best pick-ups
There were `r nrow(activity_info)` players added last week. Which was the **best pick-ups**?

```{r,echo=FALSE}
kable(activity_info %>% arrange(-Points)) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

The resurgent Sam Darnold.

### Best team performances

Here's a list of the **top five scoring performances** so far this season.

```{r, echo=FALSE}
kable(arrange(toppoints,-Score))%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```


## Looking ahead

### League standings

```{r, echo=FALSE}
kable(standings)%>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

```

Crissy remains the surprise of the season, while Scott is just behind her.

### If the season ended today...

Too early!

### This week's matchups

```{r,echo=FALSE}
kbl(nextwk1) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")
```

Good luck, y'all!